---
title: "Assignment - 1 : R Programming"
output: pdf_document
Author : Team 08
date: "2023-02-04"
editor_options: 
  chunk_output_type: console
---
**Team Number: 08 **

* Ashwin Bezliel Mathew (101415428)
* Zeel Malaviya (101420088)
* Aditya Anupam Shukla (101421678)
* Areeba Zubair (101455510)
* Jasleen Kaur Arora(101412147)
* Ishita Saha (101396418)


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## DATASET

The Data set Choose for the analysis is Employee data set named "Employee_Data"

To import and view the data set 

```{r}
library(tidyverse)
library(readxl)
Employee_data <- read_excel("Employee_data.xlsx")
View(Employee_data)

```

## ANALYSIS

**1) Print the structure of your dataset**

  Ans: To print the Structure of the data set 

```{r}
str(Employee_data)
```

**2) List the variables in your dataset**
  
  Ans:
```{r}
colnames(Employee_data)
```

**3) Print the top 15 rows of your dataset **

  Ans:
```{r}
head(Employee_data,15)
```

**4) Write a user defined function using any of the variables from the data set**

  Ans: We created a function to calculate average age

```{r}
calculate_average_Age <- function(Age) 
  {
   mean(Age)
  }

average_Age <- calculate_average_Age(Employee_data$Age)
average_Age
```
**5) Use data manipulation techniques and filter rows based on any logical criteria that exist in**

  Ans: We are filtering out Employees with high bounus i.e. 40% or above

```{r}
library(dplyr)
High_Bonus <- filter(Employee_data,`Bonus %`> .39)
High_Bonus
```

**6) Identify the dependent & independent variables and use reshaping techniques and create a new data frame by joining those variables from your dataset.**

  Ans: Identify the dependent & independent variables. Let's say, dependent variable is Annual Salary and independent variables are Age and Bonus %

```{r}
dep_var <- Employee_data$`Annual Salary`
indep_vars <- Employee_data[c("Age", "Bonus %")] 
indep_vars
```
**7)  Create a new data frame by joining dependent and independent variables**

  Ans
```{r}
Employee_data_new <- cbind(dep_var, indep_vars)
head(Employee_data_new,5)
```

**8) Remove missing values in your dataset.**

  Ans:
```{r}

Employee_data_new_clean <- Employee_data_new[complete.cases(Employee_data_new),]

```

**9) Identify and remove duplicated data in your dataset**

  Ans:
```{r}
Employee_data_new_clean <- unique(Employee_data_new_clean)

```

**10) Reorder multiple rows in descending order**

  Ans:
```{r}
Employee_data_new_clean %>% head(15,) %>%arrange(desc(Age))


```
**11) Rename some of the column names in your dataset**

  Ans:
```{r}
colnames(Employee_data_new_clean) <- c("Annual_Salary", "Age", "Bonus_Percentage")

```

**12) Add new variables in your data frame by using a mathematical function (for e.g. – multiply an existing column by 2 and add it as a new variable to your data frame)**

  Ans:
```{r}
Employee_data_new_clean$Double_Annual_Salary <- 2 * Employee_data_new_clean$Annual_Salary
str(Employee_data_new_clean)
```
**13) Create a training set using random number generator engine.**

  Ans:

```{r}
set.seed(123)
training_set_index <- sample(1:nrow(Employee_data_new_clean), 0.8 * nrow(Employee_data_new_clean))
training_set <- Employee_data_new_clean[training_set_index, ]
```
**14) Print the summary statistics of your dataset**

  Ans:
```{r}
summary(Employee_data_new_clean)
```
**15) Use any of the numerical variables from the dataset and perform the following statistical functions**
• Mean
• Median
• Mode
• Range


  Ans:

### Mean
```{r}
mean(Employee_data_new_clean$Annual_Salary)
```

### Median
```{r}
median(Employee_data_new_clean$Annual_Salary)
```

### Mode
```{r}
mode(Employee_data_new_clean$Annual_Salary)
```

### Range
```{r}
range(Employee_data_new_clean$Annual_Salary)
```

**16) Plot a scatter plot for any 2 variables in your dataset**

  Ans:
```{r}

ggplot(Employee_data_new_clean, aes(x = Age, y = Annual_Salary)) + 
  geom_point() + 
  ggtitle("Scatter Plot of Age and Annual Salary")

```

**17) Plot a bar plot for any 2 variables in your dataset**

  Ans:

```{r}
ggplot(Employee_data_new_clean, aes(x = Age, fill = Annual_Salary)) + 
  geom_bar(position = "dodge") + 
  ggtitle("Bar Plot of Age and Annual Salary") + scale_color_brewer(palette="Accent")

```
**18) Find the correlation between any 2 variables by applying least square linear regression model**

  Ans:

```{r}
model <- lm(Annual_Salary ~ Age, data = Employee_data_new_clean)
summary(model)

```

